### 2023-09-18 paper/tables/integrated_yields.tex
Ton -> tonne (metric unit)
felix comments, event yields
sect 2 revised

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%-----------------------------------------------------------------
\begin{table}[t]
  \centering
  \small
  \renewcommand{\arraystretch}{1.70}
\begin{tabularx}{\textwidth}{X||c|c|c||c|c|c}
\toprule
Detector & $\quad$ $N_{\nu_e}$ $\quad$ &$\quad$ $N_{\bar{\nu}_e}$$\quad$   &   $N_{\nu_e} + N_{\bar{\nu}_e}$ &
$\quad$$N_{\nu_\mu}$ $\quad$ & $\quad$ $N_{\bar{\nu}_\mu}$ $\quad$  &   $N_{\nu_\mu} + N_{\bar{\nu}_\mu}$ \\
\midrule
\midrule
FASER$\nu$  & 0.2k (31)    & 110 (19)  & 0.3k (50)  &  0.6k (98)  &  0.3k (45)  &  0.9k (140) \\
SND@LHC  &  88 (11)  & 38 (5.4)    & 130 (16)   &  0.3k (54) & 96 (22)   &  0.4k  (76)\\
\midrule
\midrule
FASER$\nu$2  & 58k (8.3k)   & 28k (5.0k)   & 86k (13.3k)  & 190k (27k)  & 67k (12k)    & 260k (39k)   \\
AdvSND-far  &  5.9k (0.7k)  & 2.8k (0.4k)   & 8.7k (1.1k)  & 20k (2.4k)  & 8k (1.1k)   & 28k (3.5k)   \\
FLArE10 & 22k (2.7k) & 10k (1.5k)   &  32k (4.2k) &  38k (5.2k)&   19k (2.5k) &   57k (7.7k) \\
FLArE100 &   140k (18k)         &    66k (9.5k)         &       210k (27k)       &   220k (30k)      &  120k (15k)    &  340k (45k)  \\
  \bottomrule
\end{tabularx}
\vspace{0.2cm}
\caption{\small Integrated event yields for the six detectors considered,
  separated into electron neutrinos and antineutrinos,
  muon neutrinos and antineutrinos, and their sum.
  %
  These event yields are computed from Eq.~(\ref{eq:event_yields_calculation})
  imposing DIS kinematics, $Q^2 \ge 2$ GeV$^2$ and $W^2 \ge 4$ GeV$^2$.
  %
 The numbers in parenthesis indicate the event rates corresponding to charm
 production.
 %
 In the case of the FLArE detector, we display results for two proposed
 options with fiducual masses of 10 and 100 tons respectively.
  \label{tab:integrated_rates}
}
\end{table}
%-----------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%-----------------------------------------------------------------
\begin{table}[t]
  \centering
  \small
  \renewcommand{\arraystretch}{1.70}
\begin{tabularx}{\textwidth}{X||c|c|c||c|c|c}
\toprule
Detector & $\quad$ $N_{\nu_e}$ $\quad$ &$\quad$ $N_{\bar{\nu}_e}$$\quad$   &   $N_{\nu_e} + N_{\bar{\nu}_e}$ &
$\quad$$N_{\nu_\mu}$ $\quad$ & $\quad$ $N_{\bar{\nu}_\mu}$ $\quad$  &   $N_{\nu_\mu} + N_{\bar{\nu}_\mu}$ \\
\midrule
\midrule
FASER$\nu$  & 400 (62)    & 210 (38)  & 610 (100)  &  1.3k (200)  &  500 (90)  &  1.8k (290) \\
SND@LHC  &  180 (22)  & 76 (11)    & 260 (32)   &  510 (59) & 190 (25)   &  700  (83)\\
\midrule
\midrule
FASER$\nu$2  & 116k (17k)   & 56k (9.9k)   & 170k (27k)  & 380k (53k)  & 133k (23k)    & 510k (76k)   \\
AdvSND-far  &  12k (1.5k)  & 5.5k (0.82k)   & 18k (2.3k)  & 40k (4.8k)  & 16k (2.2k)   & 56k (7k)   \\
FLArE10 & 44k (5.5k) & 20k (3.0k)   &  64k (8.5k) &  76k (10k)&   38k (5.0k) &   110k (15k) \\
FLArE100 &   290k (35k)         &    130k (19k)         &       420k (54k)       &   440k (60k)      &  232k (30k)    &  670k (90k)  \\
  \bottomrule
\end{tabularx}
\vspace{0.2cm}
\caption{\small Integrated event yields for the six detectors considered,
  separated into electron neutrinos and antineutrinos,
  muon neutrinos and antineutrinos, and their sum.
  %
  These event yields are computed from Eq.~(\ref{eq:event_yields_calculation})
  imposing DIS kinematics, $Q^2 \ge 2$ GeV$^2$ and $W^2 \ge 4$ GeV$^2$.
  %
 The numbers in parenthesis indicate the event rates corresponding to charm
 production, Eq.~(\ref{eq:event_yields_charm}).
 %
 In the case of the FLArE detector, we display results for two proposed
 options with fiducual masses of 10 and 100 tonnes respectively.
  \label{tab:integrated_rates}
}
\end{table}
%-----------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
